### 2014-10-31 fundamentals/impl.tex
went with open source, cuz google

\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
Furthermore, the core infrastructure and related archetypes are free and 
open-source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. It can be easily deployed 
on large computer systems, such as \acrlong{HTC} systems.

@@

In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open-source archetypes. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.

>>>>

\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
Furthermore, the core infrastructure and related archetypes are free and 
open source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. It can be easily deployed 
on large computer systems, such as \acrlong{HTC} systems.

@@

In particular, since the clean plug-in architecture loads libraries without any
modifications to the \Cyclus kernel, closed-source archetypes can be used with
the simulator alongside open source archetypes. This architecture
allows closed-source libraries (e.g., those representing sensitive nuclear
processes and subject to export control) to be developed and licensed privately.
